Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
proofreading Sections 1,2,3

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
\newcommand{\arcof}{\operatorname{\alpha}} % arc of a vertex
\newcommand{\dualarcof}{\operatorname{\alpha}\dual} % dual arc of a vertex
\newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
\newcommand{\ZZZ}{\mathsf{Z}} % Z

@@

\section{Introduction}
\pierreguy{Should we talk of g,c,d-vectors in the abstract?}
\vincent{No. I would say that this does not need to be emphasized.}
The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).

@@

%We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.

\begin{definition}[\cite{ButlerRingel}]
\label{def:gentleQuiver}
A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver such that
\begin{itemize}
\item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{itemize}
The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
\end{definition}

\begin{definition}[\cite{PaluPilaudPlamondon}]
\label{def:blossomingQuiver}
A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$v \in Q_0$ is incident to either one ($v$ is a leaf) or four arrows ($v$ is an internal vertex).
The \defn{pruned subquiver} of a quiver $\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
\end{definition}

@@

\begin{definition}
\label{def:string}
Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
A \defn{finite string} for~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{itemize}
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{itemize}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
%We usually denote strings by~$\rho, \sigma, \tau$.
%We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
%\(
%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}
%\)
%the set of \defn{almost positive unoriented strings}.
%Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.
%\end{enumerate}
\end{definition}

\begin{definition}
 An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
\end{definition}

\begin{notation}
If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
\begin{itemize}
 \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
 \item $c^\infty$ for the infinite word~$c c c\cdots$,
% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
 \item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
\end{itemize}
We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.
\end{notation}

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite chord.
%In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
\end{definition}

@@

\begin{definition}
\label{def:topBottom}
The substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'-1} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'+1} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'-1} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'+1} = 1$).
In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
We use the same notations for undirected walks.
\end{definition}

@@

We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{PaluPilaudPlamondon}.
We start with the kissing relation for walks.

\begin{definition}
\label{def:kiss}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$ contains a \emph{finite} substring.
See \fref{fig:kissing}.
% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
\vincent{Can we delete this notation.}
%
\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=1]{kissing}}
	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
	\label{fig:kissing}
\end{figure}
%
\end{definition}

\begin{definition}
\label{def:nKc}
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
Note that self-kissing walks never appear in~$\NKC$ by definition.
In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-crossing bended walks of~$\bar Q$.
\end{definition}

@@

\begin{definition}
A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
For~$V \subset \surface$,
\begin{itemize}
\item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$.
\end{itemize}
As usual, curves and arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
\end{definition}

@@

\begin{definition}
A \defn{dissection} of~$\bar\surface$ is a collection~$\dissection$ of pairwise non-crossing arcs on~$\bar\surface$.
The \defn{edges} of~$\dissection$ are its arcs together with the boundary arcs of~$\bar\surface$.
The \defn{faces} of~$\dissection$ are the connected components of the complement of the union of the edges of~$\dissection$ in the surface~$\surface$.
We denote by~$\vertices(\dissection)$, $\edges(\dissection)$ and~$\faces(\dissection)$ the sets of vertices, edges and faces of~$\dissection$ respectively.
The dissection~$\dissection$ is \defn{cellular} if all its faces are disks.
For~$V \subseteq M$, a \defn{$V$-dissection} is a dissection with only $V$-arcs.
\end{definition}

@@

\begin{definition}
Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
\end{definition}

Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{dissections}}
	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual dissections on different surfaces. The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces. The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus. The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is in red.}
	\label{fig:dissections}
\end{figure}
%
Note that contrarily to the usual conventions, the dual vertex~$f\dual$ of a face~$f$ of~$\dissection$ is not always in the interior of the face~$f$.
More precisely, there are two situations:
\begin{itemize}
\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
\item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
\end{itemize}
In fact, the second point forces the following characterization of the cellular dissections that admit a dual cellular dissection.

\begin{proposition}
\label{prop:conditionsDualDissections}
For a cellular $V$-dissection~$\dissection$ of a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, the following assertions are equivalent:
\begin{enumerate}[(i)]
\item there exists a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
\item each face of~$\dissection$ contains exactly one point of~$V\dual$.
\end{enumerate}
Moreover, the cellular dissection~$\dissection\dual$ is uniquely determined.
\end{proposition}

@@

\begin{definition}
%Interior points, blossom points.
%Half-arcs.
We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$V \cup V\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.
See \eg Figures~\ref{fig:accordions} and~\ref{fig:slaloms}.
\end{definition}

@@

\begin{remark}
In Definition~\ref{def:accordion}, observe that
\begin{itemize}
\item the edges of~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ might coincide, see ...
\item the second condition is automatically satisfied if~$f\dual$ is not a puncture.
\end{itemize}
\end{remark}

@@

>>>>

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
\newcommand{\arcof}{\operatorname{\varepsilon}} % arc of a vertex
\newcommand{\dualarcof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
\newcommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
\newcommand{\ZZZ}{\mathsf{Z}} % Z

@@

\section{Introduction}
\pierreguy{Should we talk of g,c,d-vectors in the abstract?}
\vincent{No. I would say that this does not need to be emphasized.}
The aim of this paper is to prove that two combinatorial objects, called the ``non-kissing complex'' and the ``non-crossing complex'', are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).

@@

%We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
The following definition is adapted from~\cite{ButlerRingel}.

\begin{definition}%[\cite{ButlerRingel}]
\label{def:gentleQuiver}
A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver~where
\begin{enumerate}[(i)]
\item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{enumerate}
The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
\end{definition}

\begin{definition}%[\cite{PaluPilaudPlamondon}]
\label{def:blossomingQuiver}
A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$v \in Q_0$ is incident to either one ($v$ is a leaf) or four arrows ($v$ is an internal vertex).
The \defn{pruned subquiver} of a quiver $\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
\end{definition}

@@

\begin{definition}
\label{def:string}
Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
A \defn{finite string} in~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{itemize}
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{itemize}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
%We usually denote strings by~$\rho, \sigma, \tau$.
%We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
%\(
%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}
%\)
%the set of \defn{almost positive unoriented strings}.
%Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.
%\end{enumerate}
\end{definition}

\begin{definition}
 An oriented cycle~$c$ in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$ is called \defn{primitive} if it cannot be written as an $n$th power ($n>1$) of a cycle.
\end{definition}

\begin{notation}
If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
\begin{itemize}
\item $c^\infty$ for the infinite word~$c c c\cdots$,
\item ${}^\infty c$ for the infinite word~$\cdots c c c$,
% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
\item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
\end{itemize}
We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.
\end{notation}

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
%In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
\end{definition}

@@

\begin{definition}
\label{def:topBottom}
We say that the substring~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ is \defn{at the bottom} (resp.~\defn{on top}) of the walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ if~$i'=-\infty$ or~$\varepsilon_{i'-1} = 1$ and~$j'=+\infty$ or~$\varepsilon_{j'+1} = -1$ (resp.~if~$i'=-\infty$ or~$\varepsilon_{i'-1} = -1$ and~$j'=\infty$ or~$\varepsilon_{j'+1} = 1$).
In other words the (at most) two arrows of~$\omega$ incident to the endpoints of~$\sigma$ point towards~$\sigma$ (resp.~outwards from~$\sigma$).
We denote by~$\Sigma_\bottom(\omega)$ and~$\Sigma_\top(\omega)$ the sets of bottom and top substrings of~$\omega$ respectively.
We use the same notations for undirected~walks.
\end{definition}

@@

We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon}.
We start with the kissing relation for walks.

\begin{definition}%[\cite{McConville, PaluPilaudPlamondon}]
\label{def:kiss}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')$ contains a \emph{finite} substring.
See \fref{fig:kissing}.
% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the commmon finite substring is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
\vincent{Can we delete this notation.}
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissing}}
	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
	\label{fig:kissing}
\end{figure}
%
\end{definition}

\begin{definition}%[\cite{McConville, PaluPilaudPlamondon}]
\label{def:nKc}
The \defn{non-kissing complex} of~$\bar Q$ is the simplicial complex~$\NKC$ whose faces are the collections of pairwise non-kissing walks of~$\NKWalks^\pm(\bar Q)$.
Note that self-kissing walks never appear in~$\NKC$ by definition.
In contrast, no straight walk can kiss another walk by definition, so that they appear in all facets of~$\NKC$.
The \defn{reduced non-kissing complex}~$\RNKC$ is the simplicial complex whose faces are the collections of pairwise non-kissing bended walks of~$\bar Q$.
\end{definition}

@@

\begin{definition}
A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
For~$V \subset \surface$,
\begin{itemize}
\item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$, and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
\end{itemize}
As usual, curves and arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
\end{definition}

@@

\begin{definition}
A \defn{dissection} of~$\bar\surface$ is a collection~$\dissection$ of pairwise non-crossing arcs on~$\bar\surface$.
The \defn{edges} of~$\dissection$ are its arcs together with the boundary arcs of~$\bar\surface$.
The \defn{faces} of~$\dissection$ are the connected components of the complement of the union of the edges of~$\dissection$ in the surface~$\surface$.
We denote by~$\vertices(\dissection)$, $\edges(\dissection)$ and~$\faces(\dissection)$ the sets of vertices, edges and faces of~$\dissection$ respectively.
The dissection~$\dissection$ is \defn{cellular} if all its faces are topological disks.
For~$V \subseteq M$, a \defn{$V$-dissection} is a dissection with only $V$-arcs.
\end{definition}

@@

\begin{definition}
Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, both denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
\end{definition}

Some examples of dual cellular dissections on different surfaces are represented in \fref{fig:dissections}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{dissections}}
	\caption{Some pairs~$(\dissection, \dissection\dual)$ of dual cellular dissections on different surfaces. The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces. The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus. The dissection~$\dissection$ is in green while its dual dissection~$\dissection\dual$ is~in~red.}
	\label{fig:dissections}
\end{figure}
%
Note that contrarily to the usual conventions, the dual vertex~$f\dual$ of a face~$f$ of~$\dissection$ is not always in the interior of the face~$f$.
More precisely, there are two situations:
\begin{itemize}
\item if a face~$f$ has no edge on the boundary of~$\surface$, its dual vertex~$f\dual$ lies in the interior~of~$f$,
\item if a face~$f$ has an edge on the boundary of~$\surface$, then it has exactly one such edge and its dual vertex~$f\dual$ lies on this edge.
\end{itemize}
In fact, the second point forces the following characterization of the cellular dissections that admit a dual cellular dissection.

\begin{proposition}
\label{prop:conditionsDualDissections}
For a cellular $V$-dissection~$\dissection$ of a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, the following assertions are equivalent:
\begin{enumerate}[(i)]
\item there exists a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ such that~$\dissection$ and~$\dissection\dual$ are dual cellular dissections,
\item each face of~$\dissection$ contains exactly one point of~$V\dual$ (in particular, at most one boundary edge).
\end{enumerate}
Moreover, the cellular dissection~$\dissection\dual$ is uniquely determined.
\end{proposition}

@@

\begin{definition}
%Interior points, blossom points.
%Half-arcs.
We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$V \cup V\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.
See \eg Figures~\ref{fig:accordions} and~\ref{fig:slaloms} where the blossom points appear as white hollow vertices.
\end{definition}

@@

\begin{remark}
In Definition~\ref{def:accordion}, observe that
\begin{itemize}
\item the edges of~$a$ and~$b$ of~$f$ crossed by~$\alpha$ might coincide, see ...
\item the second condition is automatically satisfied if~$f\dual$ is not a puncture, \ie when it lies on the boundary of~$\surface$.
\end{itemize}
\end{remark}

@@

\begin{example}
\vincent{Example with the disk}
\end{example}
